### 2021-02-25 architecture.tex
Remove some content to shorten the text

The graph representation has the following properties:
\begin{itemize}
\item Lossless: The original problem can be faithfully reconstructed from the corresponding graph representation
(up to logical equivalence).
\item Signature agnostic: Renaming the symbols and variables in the input problem yields an isomorphic graph.
\item For each relation $r \in \mathcal{R}$, its inverse $\inv{r}$ is also present in the graph,
typically\todo{MS: jaka je vyjimka?} represented by a different edge type.
\todo{MS: tohle jsem nepochopil. Nemuzeme rict, ze (az na nejakou vyjimkou) jsou edges v obou smerech?\\
FB: Chci vyjasnit, ze inverzni edge ma jiny edge type.}
\item A singleton node of type \ntype{problem} is connected to all the clauses of the problem.
\item The polarity of the literals is expressed by the type of the edge (\epos{} or \eneg{})
connecting the respective atom to the clause it occurs in.
\item For every non-equality atom and term, the order of its arguments is captured by a sequence of \ntype{argument} nodes chained by edges \cite{Rawson2020}.
\item The two operands of equality are not ordered.
This reflects the symmetry of equality.
\item Sub-expression sharing \cite{Chvalovsky2019,Olsak2019,Rawson2020}:
\todo[inline]{MS: (Almost)}
\todo[inline]{MS: Predpokladam ze dva ruzne ground literaly p(c) tam budou taky jen jendnou?\\
FB: Literaly nemaji nody. Atomy maji nody a polarita literalu je zakodovana v typu hrany, ktery jej spojuje s klauzuli.
MS: O to my, neslo. Slo o to, jestli se sdily ground termy mezi klauzulemi, ted uz dobry! :)}
Identical atoms and terms share a node representation.
\todo{FB: Cite some text about sub-expression sharing. Perhaps Rawson2020?}
\todo{MS: Ale mezitim se to tu zmenilo a ja prestavam chapat, co je ``Redundant''!}
Note that since each variable is bound by a clause,
ground terms are shared across clauses,
but non-ground terms are only shared within the context of a clause.
\todo{FB: Remove as of little interest?}
\end{itemize}
\todo{FB: Reference appendix if we describe the representation in more detail there.}
\todo{FB: Mention other encodings that have been proposed by Mirek and Michael and compare ours to theirs.}

>>>>

The graph representation has the following properties:
\begin{itemize}
\item Lossless: The original problem can be faithfully reconstructed from the corresponding graph representation
(up to logical equivalence).
\item Signature agnostic: Renaming the symbols and variables in the input problem yields an isomorphic graph.
\item For each relation $r \in \mathcal{R}$, its inverse $\inv{r}$ is also present in the graph,
typically\todo{MS: jaka je vyjimka?} represented by a different edge type.
\todo{MS: tohle jsem nepochopil. Nemuzeme rict, ze (az na nejakou vyjimkou) jsou edges v obou smerech?\\
FB: Chci vyjasnit, ze inverzni edge ma jiny edge type.}
%\item A singleton node of type \ntype{problem} is connected to all the clauses of the problem.
\item The polarity of the literals is expressed by the type of the edge (\epos{} or \eneg{})
connecting the respective atom to the clause it occurs in.
\item For every non-equality atom and term, the order of its arguments is captured by a sequence of \ntype{argument} nodes chained by edges \cite{Rawson2020}.
\item The two operands of equality are not ordered.
This reflects the symmetry of equality.
\item Sub-expression sharing \cite{Chvalovsky2019,Olsak2019,Rawson2020}:
\todo[inline]{MS: (Almost)}
\todo[inline]{MS: Predpokladam ze dva ruzne ground literaly p(c) tam budou taky jen jendnou?\\
FB: Literaly nemaji nody. Atomy maji nody a polarita literalu je zakodovana v typu hrany, ktery jej spojuje s klauzuli.
MS: O to my, neslo. Slo o to, jestli se sdily ground termy mezi klauzulemi, ted uz dobry! :)}
Identical atoms and terms share a node representation.
\todo{FB: Cite some text about sub-expression sharing. Perhaps Rawson2020?}
\todo{MS: Ale mezitim se to tu zmenilo a ja prestavam chapat, co je ``Redundant''!}
%Note that since each variable is bound by a clause,
%ground terms are shared across clauses,
%but non-ground terms are only shared within the context of a clause.
\todo{FB: Remove as of little interest?}
\end{itemize}
\todo{FB: Reference appendix if we describe the representation in more detail there.}
\todo{FB: Mention other encodings that have been proposed by Mirek and Michael and compare ours to theirs.}
